Combinatorial Proofs and Decomposition Theorems for First-order Logic

### 2021-01-11 main.tex
small change
Add missing references

For a formula $A$, we can define its
associated fograph $\graphof(A)$ inductively by: 
\begin{equation*}
  \begin{array}{cc}
    \graphof{\alpha} = \single \alpha & 
    \graphof{\forall x . A} = \single x + \graphof{A} \\[.5ex]
    \graphof{A \cor B} = \graphof{A} + \graphof{B} &
    \graphof{\exists x . A} = \single x \times \graphof{A} \\[.5ex]
    \graphof{A \cand B} = \graphof{A} \times \graphof{B} &

@@

\begin{proof}
  \todo{}
\end{proof}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

We consider here only the cut-free fragment, as cut-elimination for
deep inference systems has already been discussed
elsewhere~\cite{brunnler:,alertubella:}.\footnote{In the deep
inference literature, the cut-free fragment is also called the
\emph{down-fragment}. But as we do not discuss the \emph{up-fragment}
here, we omit the down-arrows $\downarrow$ in the rule names.}

>>>>

For a formula $A$, we can define its
associated fograph $\graphof{A}$ inductively by:
\begin{equation*}
  \begin{array}{cc}
    \graphof{\alpha} = \single \alpha & 
    \graphof{\forall x . A} = \single x + \graphof{A} \\[.5ex]
    \graphof{A \cor B} = \graphof{A} + \graphof{B} &
    \graphof{\exists x . A} = \single x \times \graphof{A} \\[.5ex]
    \graphof{A \cand B} = \graphof{A} \times \graphof{B} &

@@

\begin{proof}
  \todo{}
  By a straightforward induction on $A$.
\end{proof}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

We consider here only the cut-free fragment, as cut-elimination for
deep inference systems has already been discussed
elsewhere~\cite{brunnler:06:herbrand,alertubella:guglielmi:18}.
\juihsuan{references added. Please check if they are the right ones.}
\footnote{In the deep
inference literature, the cut-free fragment is also called the
\emph{down-fragment}. But as we do not discuss the \emph{up-fragment}
here, we omit the down-arrows $\downarrow$ in the rule names.}
